Formal Analysis of EDHOC Key Establishment for Constrained IoT Devices

### 2022-07-19 formalization.tex
[add] update of protocol description

On top of the Dolev-Yao model, we allow the adversary two extra capabilities with respect to getting access to the long-term and ephemeral keys. 
%
Long-term key reveal, denoted $\mRevLTK^{t}(A)$, stands for the adversary gaining access to a principal $A$'s long-term private key \mPriv{A} at a time point $t$.
%
Ephemeral key reveal, denoted $\mRevEph^{t}(A, k)$, stands for the adversary obtaining, at time $t$, the ephemeral private key \mPrivE{A} used by party $A$  in a session where they establish key material $k$.
%
Ephemeral keys might be stored in a less secure part of a device, but long-term keys are often stored and operate within a secure model, like a trusted execution environment (TEE). \vnote{Do we want to say more about TEEs here?}
%
Formalizing these two events allows us to have more fine-grained control over the access that an adversary has to these fundamentally different kinds of keys.
%

@@

To model the reveal of long-term keys and ephemeral keys to an adversary, we use standard reveal rules and events of type \mRevLTK{} and \mRevEph, respectively. 
%
It is also important to keep track of the time points at which these events occur.
%
Long-term keys can be revealed on registration, even before the protocol begins.
%
However, ephemeral keys in our model can only be revealed when a principal completes their role, i.e. simultaneous with events of type \mIComplete{} and \mRComplete.
%
While we did try to reveal ephemeral keys at the start of protocol execution, we could not get the verification to terminate in such a model.
\vnote{Do we still not get \mTamarin{} to terminate if we reveal ephemeral keys at the start of the protocol? With the TEEs etc?}
%
Having set out the capabilities of the adversary, we now model the execution of the honest agents' roles.

>>>>

On top of the Dolev-Yao model, we allow the adversary two extra capabilities with respect to getting access to the long-term and ephemeral keys. 
%
Long-term key reveal, denoted $\mRevLTK^{t}(A)$, stands for the adversary
gaining access to a party $A$'s long-term private key \mPriv{A} at a time point $t$.
%
Ephemeral key reveal, denoted $\mRevEph^{t}(A, k)$, stands for the adversary obtaining, at time $t$, the ephemeral private key \mPrivE{A} used by party $A$  in a session where they establish key material $k$.
%
Ephemeral keys might be stored in a less secure part of a device, but long-term keys are often stored and operate within a secure model, like a trusted execution environment (TEE). \vnote{Do we want to say more about TEEs here?}
%
Formalizing these two events allows us to have more fine-grained control over the access that an adversary has to these fundamentally different kinds of keys.
%

@@

To model the reveal of long-term keys and ephemeral keys to an adversary, we use standard reveal rules and events of type \mRevLTK{} and \mRevEph, respectively. 
%
It is also important to keep track of the time points at which these events occur.
%
Long-term keys can be revealed on registration, even before the protocol begins.
%
However, ephemeral keys in our model can only be revealed when a party completes their role, i.e. simultaneous with events of type \mIComplete{} and \mRComplete.
%
While we did try to reveal ephemeral keys at the start of protocol execution, we could not get the verification to terminate in such a model.
\vnote{Do we still not get \mTamarin{} to terminate if we reveal ephemeral keys at the start of the protocol? With the TEEs etc?}
%
Having set out the capabilities of the adversary, we now model the execution of the honest agents' roles.
